Universal Anonymous Signatures

### 2022-05-05 prism-backend/research/gsac/construction-uas.tex
Making a pass.

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. In \secref{sec:instantiation}, we give a concrete
instantiation.

We use three different NP relations in our generic construction. Namely,
$\NIZKRel_{\Issue}$ for issuance, $\NIZKRel_{\Sign}$ for signing, and
$\NIZKRel_{\Inspect}$ for inspection. We will be defining them in the
corresponding protocol/algorithm.

\todo{Many variables need renaming here.}

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
The setup process essentially consists on generating the public parameters
for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
\NIZKsecpar,\SBCMsecpar,\Esecpar)$. Then, run $\Cparm \gets
\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Inspect} \gets
\NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},
\AttrSpace)$

@@

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
To generate its key pair, each inspector first parses \parm as $(\cdot,\cdot,
\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
(\Ssk,\Edk)$. Finally, returns $(\opk,\osk)$.

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
The protocol is run between an issuer, and a user with secret key \usk and
credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. For readability we write $\attrs_{\scred}$ as abbreviation for
$\lbrace \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for
$\sipk_{\scred}$. The user requests a signature on a commitment to the user key,
as well as on the attributes in \attrs. In addition, the user proves that the
issuance function \fissue established by the issuer is satisfied by the
credentials in $\scred$
and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
(\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom = \CCommit(usk) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,
\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
for a user to obtain a credential from an issuer of the system is then simply an
execution of the interactive signing protocol of an \SBCM scheme, where the user
runs $\SBCMCom(\ipk,\usk,\attrs)$, and the issuer runs $\SBCMSign(\isk,\attrs)$;
in both cases, using $\NIZKRel_{\Issue}$ as \NIZK relation.

@@

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of the following relation:
$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,\feval,
\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land \yeval =
\feval(\usk,\scred,\msg) \land
\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
\rbrace$ where, for each $\cred \in \scred$, $\attrs_{\cred}$ and $\ipk_{\cred}$,
as well as $\attrs_{\scred}$ and $\sipk_{\scred}$ are as in $\langle \Obtain,
\Issue \rangle$.
%
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the inspection policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval;r)$ for some fresh randomness $r$.
Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek))$ and
outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.

@@

\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
  \Inspect(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
We first define NIZK relation $\NIZKRel_{\Inspect} = \lbrace (\osk),(\Ec,\yinsp)
: \yinsp = \EDec(\osk,\Ec) \rbrace$.
%
For inspection, the inspector first verifies the signature by running $\Verify(
\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
\sig as $(\NIZKproof,\Ec)$, decrypts \Ec by running $\yeval \gets \EDec(\osk,
\Ec)$, and computes $\NIZKproof_{\Inspect} \gets \NIZKProve^{\NIZKRel_{\Inspect}}
(\NIZKcrs_{\Inspect},\osk,(\Ec,\yinsp))$. It returns $(\yinsp,
\NIZKproof_{\Inspect})$.

\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
To assess the validity of an inspection proof, first check the signature
by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
parse \sig as $((\cdot,\Ec),\cdot)$ and verify \NIZKproof with $\NIZKVerify
(\NIZKcrs_{\Inspect},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
passes, and reject otherwise.

>>>>

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. In \todo{\secref{sec:instantiation}}, we give a concrete
instantiation.

We use three different NP relations in our generic construction. Namely:

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs the rules for issuing
  new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs what utility information is directly revealed
  by signatures. It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec =
  \EEnc(\Eek,\yinsp;r) \land \yeval = \feval(\usk,\scred,\msg) \land
  \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$, with
  $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Set by openers, governs the utility information
  to be extracted by the \Open algorithm. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$. It proves
  that the decryption of the opening utility value has been done correctly.
\end{description}

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
The setup process essentially consists on generating the public parameters
for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
\NIZKsecpar,\SBCMsecpar,\Esecpar)$. Then, run $\Cparm \gets
\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Open} \gets
\NIZKSetup^{\NIZKRel_{\Open}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open},
\AttrSpace)$. Note that many of these parameter setup algorithms can
actually be run by separate entities (respecting some commonalities like,
e.g., same pairing-friendly curves). For instance, each opener could
run its own \ESetup algorithm, or each verifier its
$\NIZKSetup^{\NIZKRel_{\Sign}}$, to advertise the signing evaluation functions
it accepts. For simplicity of exposition, we bundle them together here.

@@

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
To generate its key pair, each opener first parses \parm as $(\cdot,\cdot,
\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
(\Ssk,\Edk)$. Finally, returns $(\opk,\osk)$.

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
The protocol is run between an issuer, and a user with secret key \usk and
credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. The user requests a signature on a commitment to the user key,
as well as on the attributes in \attrs. In addition, the user proves that the
issuance function \fissue established by the issuer is satisfied by the
credentials in $\scred$
and its user secret key. For this, we use relation $\NIZKRel_{\Issue}$, as
defined above. The interactive protocol for a user to obtain a credential from
an issuer of the system is then simply an execution of the interactive signing
protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\attrs)$,
and the issuer runs $\SBCMSign(\isk,\attrs)$; in both cases, using
$\NIZKRel_{\Issue}$ as \NIZK relation. The credential \cred produced by the user
is the result of the interactive signing protocol, and the \utrans entry for
the issuer is its transcript which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.

@@

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
% 
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the opening policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval;r)$ for some fresh randomness $r$.
Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek))$ and
outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.

@@

\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
  \Open(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
Here we leverage relation $\NIZKRel_{\Open}$.
%
To open a signature, the opener first verifies the signature by running $\Verify
(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
\sig as $(\NIZKproof,\Ec)$, decrypts \Ec by running $\yeval \gets \EDec(\osk,
\Ec)$, and computes $\NIZKproof_{\Open} \gets \NIZKProve^{\NIZKRel_{\Open}}
(\NIZKcrs_{\Open},\osk,(\Ec,\yinsp))$. It returns $(\yinsp,
\NIZKproof_{\Open})$.

\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
To assess the validity of an opening proof, first check the signature
by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
parse \sig as $((\cdot,\Ec),\cdot)$ and verify \NIZKproof with $\NIZKVerify
(\NIZKcrs_{\Open},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
passes, and reject otherwise.

### 2022-05-05 prism-backend/research/gsac/extensions-gsac.tex
Making a pass.

\GSAC is a direct combination of group signatures and anonymous credentials.
%
On the one hand, by restricting to credentials without attributes (i.e., where
the only attribute is the user secret key), we get a vanilla group signature
scheme. Although, strictly, our scheme allows users to fetch more than one
credential -- which goes beyond vanilla group signatures -- this can be
trivially ``compensated'' by requiring users to prove ownership of a
conventional digital identity during the $\langle \Obtain,\Issue \rangle$
protocol\footnote{This is indeed common practice, but also frequently ommitted
  in research papers.}.
%
On the other hand, by instantiating a \GSAC scheme and simply
throwing out the opener's key pair (thus, making \Open and \Judge useless), one
gets a vanilla anonymous credential system. Or, keeping \osk, one can build an
anonymous credential system with blacklisting, which can be directly built via
the \Open function.

>>>>

\GSAC is a direct combination of group signatures and anonymous credentials.
%
On the one hand, by restricting to credentials without attributes (i.e., where
the only attribute is the user secret key), we get a vanilla group signature
scheme. Although, strictly, our scheme allows users to fetch more than one
credential -- which goes beyond vanilla group signatures -- this can be
trivially ``compensated'' by requiring users to prove ownership of a
conventional digital identity during the $\langle \Obtain,\Issue \rangle$
protocol\footnote{This is indeed common practice, but also frequently ommitted
  in research papers.}.
%
On the other hand, by instantiating a \GSAC scheme and simply
throwing out the opener's key pair (thus, making \Open and \Judge useless), one
gets a vanilla anonymous credential system. Or, keeping \osk, one can build an
anonymous credential system with blacklisting, which can be directly built via
the \Open function -- although at the cost of fully de-anonymizing blacklisted
credentials, which is much more invasive than just blacklisting.

### 2022-05-05 prism-backend/research/gsac/model-gsac.tex
Making a pass.

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
  \parm, returns the issuer's key pair. Hereafter, we assume that the public
  part \ipk is added to the group public key \gpk.
\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
  \parm, returns an opener's key pair. Hereafter, we assume that the public part
  \opk is added to the group public key \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle$.]
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred with attributes \Attrs, by
  communicating with an issuer, with private key \isk, running the \Issue
  counterpart. The user outputs the produced credential \cred, while the issuer
  outputs the protocol transcript \utrans for the produced credential.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\DAttrs,\msg)$.] The user with
  with secret key \usk, who obtained a credential \cred, produces a signature
  \sig over message \msg, revealing subset of attributes \DAttrs in \cred.
\item[$1/0 \gets \Verify(\gpk,\sig,\DAttrs,\msg)$.] Checks whether \sig is a
  valid signature revealing the attribute set \DAttrs of its signing credential,
  over message \msg.
\item[$(\upk,\oproof)/\bot \gets
  \Open(\gpk,\osk,\sig,\DAttrs,\msg)$.]
  Given a signature \sig over message \msg, produced by a credential with
  attributes containing the set \DAttrs, returns the public key \upk of the
  signer, and a proof of opening correctness \oproof; or $\bot$ if the
  opening process fails.
\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,
  \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
  the user with key \upk generated signature \sig over message \msg, revealing
  attributes $\DAttrs$. 
\end{description}

@@

\paragraph{Correctness.} %
Correctness of \GSAC schemes is formalized through the experiment in
\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
revealing attributes \DAttrs, which was honestly produced through a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \Attrs such that $\DAttrs \subseteq \Attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

@@

\begin{figure}[htp!]
  \procedure{$\ExpGSACCorrect(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
    (\cid,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
    \pcif \DAttrs \nsubseteq \ATTR[\cid] :
    \pcreturn \bot \\
    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
    \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \\
     \pcind \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Correctness experiment for \GSAC schemes.}
  \label{fig:exp-gsac-corr}
\end{figure}

@@

\paragraph{Traceability.} %
Traceability is one of the unforgeability-related properties in group
signatures. It captures that any signature accepted by \Verify needs to open
to one of the users that joined the group. While there is no traceability notion
in anonymous credentials, it is natural to map it to their unforgeability
property; if only because both require the issuer to be honest. Unforgeability
in anonymous credentials typically ensures that no adversary can get a verifier
to accept a credential presentation requiring a set of attributes that is not
contained in one of the credentials controlled by the adversary.
%
Our notion of traceability for \GSAC combines both requirements. It assumes an
honest issuer, as otherwise the adversary can create untraceable credentials at
will. The game then lets the adversary add honest and corrupt users, create
honest signatures, and open them. The adversary wins if, after this interaction,
is able to produce a $(\sig,\DAttrs,\msg)$ tuple that is accepted by \Verify,
but either cannot be opened, it can be opened but the proof is rejected by
\Judge, or even though it is accepted by \Judge, there is no credential
that contains the set of attributes \DAttrs. We formally define traceability in
the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\DAttrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\Attrs)
    \in \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no similar property is modelled for anonymous credentials
(see the discussion in \todo{\secref{sec:introduction}} for further detail). It
is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \GSAC schemes, in order for a user to be framed, the adversary first needs to
create a $(\sig,\DAttrs,\msg,\upk,\oproof)$ tuple such that the signature,
attributes, and message are accepted by \Verify, and which, along with the user
public key, and open correctness proof, are accepted by \Judge.
Then, the adversary wins the game if the owner of the credential is honest, but
the signature was not produced via the \SIGN oracle.

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     (\sig,\DAttrs,\msg,\upk,\oproof) \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
     \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1 \land 
     \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
     \pcind \uid \in \HU \land \sig \notin \SIG[\uid] \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-frame}
\end{figure}

>>>>

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
  \parm, returns the issuer's key pair. Hereafter, we assume that the public
  part \ipk is added to the group public key \gpk.
\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
  \parm, returns an opener's key pair. Hereafter, we assume that the public part
  \opk is added to the group public key \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle \Obtain(\gpk,\usk,\attrs),\Issue(\gpk,\isk,\attrs) \rangle$.]
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred with attributes \attrs, by
  communicating with an issuer, with private key \isk, running the \Issue
  counterpart. The user outputs the produced credential \cred, while the issuer
  outputs the protocol transcript \utrans for the produced credential.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\dattrs,\msg)$.] The user with
  with secret key \usk, who obtained a credential \cred, produces a signature
  \sig over message \msg, revealing subset of attributes \dattrs in \cred.
\item[$1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$.] Checks whether \sig is a
  valid signature revealing the attribute set \dattrs of its signing credential,
  over message \msg.
\item[$(\upk,\oproof)/\bot \gets
  \Open(\gpk,\osk,\sig,\dattrs,\msg)$.]
  Given a signature \sig over message \msg, produced by a credential with
  attributes containing the set \dattrs, returns the public key \upk of the
  signer, and a proof of opening correctness \oproof; or $\bot$ if the
  opening process fails.
\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\dattrs,
  \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
  the user with key \upk generated signature \sig over message \msg, revealing
  attributes $\dattrs$. 
\end{description}

@@

\paragraph{Correctness.} %
Correctness of \GSAC schemes is formalized through the experiment in
\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced through a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

@@

\begin{figure}[htp!]
  \procedure{$\ExpGSACCorrect(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
    (\cid,\dattrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
    \pcif \dattrs \nsubseteq \ATTR[\cid] :
    \pcreturn \bot \\
    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
    \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
    \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \\
     \pcind \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Correctness experiment for \GSAC schemes.}
  \label{fig:exp-gsac-corr}
\end{figure}

@@

\paragraph{Traceability.} %
Traceability is one of the unforgeability-related properties in group
signatures. It captures that any signature accepted by \Verify needs to open
to one of the users that joined the group. While there is no traceability notion
in anonymous credentials, it is natural to map it to their unforgeability
property; if only because both require the issuer to be honest. Unforgeability
in anonymous credentials typically ensures that no adversary can get a verifier
to accept a credential presentation requiring a set of attributes that is not
contained in one of the credentials controlled by the adversary.
%
Our notion of traceability for \GSAC combines both requirements. It assumes an
honest issuer, as otherwise the adversary can create untraceable credentials at
will. The game then lets the adversary add honest and corrupt users, create
honest signatures, and open them. The adversary wins if, after this interaction,
is able to produce a $(\sig,\dattrs,\msg)$ tuple that is accepted by \Verify,
but either cannot be opened, it can be opened but the proof is rejected by
\Judge, or even though it is accepted by \Judge, there is no credential
that contains the set of attributes \dattrs. We formally define traceability in
the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\dattrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\attrs)
    \in \CRED~\st~\dattrs \subseteq \attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no similar property is modelled for anonymous credentials
(see the discussion in \todo{\secref{sec:introduction}} for further detail). It
is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \GSAC schemes, in order for a user to be framed, the adversary first needs to
create a $(\sig,\dattrs,\msg,\upk,\oproof)$ tuple such that the signature,
attributes, and message are accepted by \Verify, and which, along with the user
public key, and open correctness proof, are accepted by \Judge.
Then, the adversary wins the game if the owner of the credential is honest, but
the signature was not produced via the \SIGN oracle.

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     (\sig,\dattrs,\msg,\upk,\oproof) \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
     \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land 
     \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 1~\land \\
     \pcind \uid \in \HU \land \sig \notin \SIG[\uid] \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-frame}
\end{figure}
